Viral Sequence Sorting Tools Evaluation

### 2022-08-10 Data/DrinkingWaterMetagenomes/identifying_viral_contigs_environmental_dw.Rmd
Created folder for testing pipeline on DW.

Please reach out to James Riddell (riddell.26@buckeyemail.osu.edu) or
Bridget Hegarty (email) regarding any issues, or open an issue on github.

@@

```{r inputs}
# dataset name for file organization and outputs for metrics file
dataset_name <- "lake_michigan"
# checkV
checkV_path <- "merged_lake_michigan_checkv_assemblies.tsv"
# VIBRANT
vibrant_path <- "merged_lake_michigan_vibrant_assemblies.tsv"
# DeepVirFinder
dvf_path <- "merged_lake_michigan_dvf_assemblies.tsv"
# Virsorter
vs_path <- "merged_lake_michigan_virsorter_assemblies.tsv"
# Virsorter2
vs2_path <- "merged_lake_michigan_vs2_assemblies.tsv"
# Kaiju
kj_path <- "merged_lake_michigan_kaiju_assemblies.tsv"
# KB cutoff
KB_CUTOFF <- 3000

>>>>

Please reach out to James Riddell (riddell.26@buckeyemail.osu.edu) or
Bridget Hegarty (beh53@case.edu) regarding any issues, or open an issue on github.

@@

```{r inputs}
# dataset name for file organization and outputs for metrics file
dataset_name <- "drinking_water"
# checkV
checkV_path <- "merged_drinking_water_checkv_assemblies.tsv"
# VIBRANT
vibrant_path <- "../Results/VIBRANT_genome_quality_contigs_3000.tsv"
# DeepVirFinder
dvf_path <- "merged_lake_michigan_dvf_assemblies.tsv"
# Virsorter
vs_path <- "merged_lake_michigan_virsorter_assemblies.tsv"
# Virsorter2
vs2_path <- "merged_lake_michigan_vs2_assemblies.tsv"
# Kaiju
kj_path <- "merged_lake_michigan_kaiju_assemblies.tsv"
# KB cutoff
KB_CUTOFF <- 3000
